\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and Sliding Window Filter

### 2014-12-30 Report/project_report.tex
More abstract stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Monkey Style Chinese Kung Fu vs. SWFfer Wet Jet

\end{abstract}

@@

\begin{table*}[t]
  \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of the MSCKF and SWF on synthetic datasets.}
  \begin{tabular}{*{11}{c}}
              && \multicolumn{4}{c}{MSCKF} & & \multicolumn{4}{c}{SWF} \B \\ \cline{3-6} \cline{8-11}
Feature Count && Pos. ARMSE    & Rot. ARMSE & ANEES     & Compute Time && Pos. ARMSE   & Rot. ARMSE     & ANEES & Compute Time \T\B \\ \hline
40            && 0.2672        & 0.1378        & 10.18  & 12.19 s      && 0.1750        & 0.0495        & 2280  & 114.3 s   \T \\
60            && 0.2550        & 0.1247        & 12.03  & 14.64 s      && 0.1687        & 0.0377        & 2093  & 175.9 s   \\
100           && 0.2304        & 0.0952        & 16.76  & 20.58 s      && 0.1755        & 0.0481        & 2013  & 245.3 s   \B \\ \hline
  \end{tabular}
  \label{tab:rmse_nees}
\end{table*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Accurate and consistent egomotion estimation is an important part of autonomous vehicles. The combination of visual and inertial sensors provides a relatively inexpensive, compact and complementary hardware suite that can be used on many ground and aerial vehicles. In this work, we compare two modern approaches to egomotion estimation: the Multi-State Costraint Kalman Filter (MSCKF) and the Sliding Window Filter (SWF). Each approach is motivated and outlined in detail with.
\end{abstract}

@@

\begin{table*}[t]
  \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of the MSCKF and SWF on synthetic datasets.}
  \begin{tabular}{*{11}{c}}
              && \multicolumn{4}{c}{MSCKF} & & \multicolumn{4}{c}{SWF (25)} \B \\ \cline{3-6} \cline{8-11}
Feature Count && Pos. ARMSE    & Rot. ARMSE & ANEES     & Compute Time && Pos. ARMSE   & Rot. ARMSE     & ANEES & Compute Time \T\B \\ \hline
40            && 0.2672        & 0.1378        & 10.18  & 12.19 s      && 0.1750        & 0.0495        & 2280  & 114.3 s   \T \\
60            && 0.2550        & 0.1247        & 12.03  & 14.64 s      && 0.1687        & 0.0377        & 2093  & 175.9 s   \\
100           && 0.2304        & 0.0952        & 16.76  & 20.58 s      && 0.1755        & 0.0481        & 2013  & 245.3 s   \B \\ \hline
  \end{tabular}
  \label{tab:rmse_nees}
\end{table*}
